---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

library(tidyverse)

```

```{css}

body{
    font-family: "Lucida Console", "Courier New", monospace;
    background-color: #fff8e7;
    padding: 20px;
}

h2{
  color: orange;
  text-align: center;
  padding: 20px;
}

p{
  padding: 10px;
}


```

## Observation of Cat Mood

I have submitted through google forms, observations of my cat's (Julian's) mood and generated bar charts as well as summary values to determine if I can trust my subjective sense of Julian's overall wellbeing, over time.

```{r}

# load in data from csv

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQyb1PQxUAxW9fkzikId_4e1XHXxfOCDldmIWagbSwuSSmBpAD2fFn1udf4dAzZlfyTDdmbJzAJoIEM/pub?gid=952851878&single=true&output=csv")


#create tibble table with new variable names.

latest_data <- rename( logged_data,
                        expression = 2,
                        mood_one = 4,
                        mood_two = 5,
                        mood_three = 6
                      )

# First bar chart, mood count of happy or sad

latest_data %>%
  ggplot() +
  geom_bar(aes(x = expression, fill = expression)) +
  labs(title = "Expression of Mood", x = "Expression", y = "Count")


# Summary count of positive expressions

happy_count <- sum(latest_data$expression == 'Happy (or positive expression)')


# Summary count of negative expressions

sad_count <- sum(latest_data$expression == 'Sad (or negative expression)')

```

There were a total of `r happy_count` happy expressions and `r sad_count` sad expressions so far that my cat Julian has expressed since the start of the data collection.

**Meaningful Interpretation of "Expression of Mood" Bar chart**

(creativity):

It is clear from the bar chart that in his current circumstances Julian is significantly happy more often than sad, approximately happy twice as often than sad. My initial subjective feeling before the data collection was that Julian was equally often as happy as sad. This means I now have more reason to feel positive about the care I am providing Julian.


I have also recorded a mood score (from 1 to 10, subjectively determined) to see if there is a pattern between his mood and days since taking his medication (he takes it 6pm once every 3 days). This has been plotted on a bar chart as a mean mood score for each day in the 3 day cycle.

```{r}

# Summary values for mean mood for each day in medicine cycle (score out of 10)

mean_one <- mean(latest_data$mood_one, na.rm = TRUE)%>%round(1)

mean_two <- mean(latest_data$mood_two, na.rm = TRUE)%>%round(1)

mean_three <- mean(latest_data$mood_three, na.rm = TRUE)%>%round(1)


# tibble table of mean moods for each day of medicine cycle

tibble_means <- tibble(
  less_than = c("1 day", "2 days", "3 days"),  
  means = c(mean_one, mean_two, mean_three)
)

# Bar chart of mean moods for each day of medicine cycle 

ggplot(tibble_means, aes(x = less_than, y = means, fill = less_than)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = c("purple", "cyan", "blue")) +
  labs(
    title = "Julian's Mood (based on day since meds)",
    x = "Less than x days since medication",
    y = "Mean mood out of 10"
  )

```


For my cat, Julian, the mean mood rating for less than one day since medication is `r mean_one` out of 10, less than two days is `r mean_two` out of 10, less than three days is `r mean_three` out of 10.

**Meaningful Interpretation of "Julian's Mood (based on day since meds)" Bar chart**

(creativity):

There are 3 ways in which the medication might affect mood:

1. It could reduce the symptoms of his condition.
2. It could have unintended hormonal interactions.
3. Julian might find the experience of having medicine administered, traumatic.

It could be one or several of these factors.

From the bar chart it appears that on day two there is a peak in overall mood. It also appears that his overall mood is slightly less on day three than day one. There is no clear evidence of a positive nor negative correlation between day in medication cycle and overall mood. His medication is of a very low dose, so the differences in overall mood could be attributed to other factors masking the medications effect. To investigate this further, It may make sense to collect data over a longer period of time as well as collect data on other factors than might affect his overall mood such as the weather or time of day.

